% !TeX root = ../main.tex

\chapter{Discussion}
\section{Summary}
Firstly, our methodological contributions are based on the incorporation of load sharing mechanisms.
Specifically, we redesign the home location estimation approach, residential shift identification, and human mobility and mobile communication network features that are commonly used when utilizing CDRs to analyze these behaviors. Moreover, we present a new research topic that derives treatments from CDRs or user profile information and examines the dynamics of treatment effects on two common behaviors, going beyond conventional correlation studies utilizing CDRs.
Finally, investigations into the impacts of residential shifts and smartphone adoption on mobility and communication behavior provide rich policy insights. For instance, our findings suggest policymakers should increase awareness of telecommunication infrastructure and urban transportation planning during large-scale population displacement and mobile technology transitions.


\section{Limitations}
A notable limitation in utilizing CDRs for home/work location inference and mobility pattern analysis is the inherent sampling bias present in the data.
CDRs only capture spatial information at discrete moments when individuals initiate or receive telecommunications, thereby providing an incomplete representation of their complete spatial-temporal trajectory.
This selective sampling characteristic potentially introduces bias into our inference methodologies.
However, according to empirical investigations by \cite{ranjan2012call} and \cite{zhao2016understanding}, while movement entropy estimates may exhibit either upward or downward bias depending on context, metrics such as radius of gyration and home/work location inferences demonstrate robust reliability.
By extension, we posit that eccentricity measurements remain relatively unbiased, as they share fundamental characteristics with radius of gyration—specifically, both metrics aim to capture the geographical shape defined by the visited locations.
Furthermore, the mobile communication network features we derive are specifically designed to quantify distinct contact behaviors, rendering them methodologically appropriate for our analytical framework despite the aforementioned sampling considerations.

Another limitation is that individuals, especially younger generations, have recently started engaging social media platforms more frequently to connect with friends and making fewer phone calls (\cite{garrett2023linking}), which may deteriorate the quality of utilizing CDRs for home/work location inference and mobility pattern analysis.
While this limitation does not affect our study since our sample period spans from 2013 to 2014, when social media platforms were not yet widespread, it raises questions about the validity of utilizing CDRs for more contemporary mobility and communication studies.
In fact, there is a growing body of research attempting to leverage geolocated posts on various social media platforms, such as Facebook (\cite{sahai2022social}), Twitter (\cite{zagheni2014inferring}, \cite{hawelka2014geo}, \cite{jurdak2015understanding}, \cite{luo2016explore}), and Weibo(\cite{cui2018social}, \cite{ebrahimpour2020analyzing}), to study migration and human mobility patterns.
Nevertheless, we still believe CDRs have their own advantages.
First, in developing countries where network infrastructures are not well-developed, people still rely on phone calls to communicate with their family and friends.
Second, people often use social media to share their travel experiences, resulting in important locations inferred from geolocated posts that potentially yield systematic biases. As stated in \cite{armstrong2021challenges}, utilizing tweets to infer migration populations yields high misclassification rates.
Finally, mobile communication is a more fundamental contact behavior, potentially leading to higher coverage of different age groups and reducing income bias due to unequal access to the internet, as Facebook users are often located in high-income regions in India (\cite{sahai2022social}).

\section{Future Work}
The main goal of this paper is to quantify the effects of residential shifts and smartphone adoption on behavioral features.
We apply the estimation method proposed by \cite{callaway2021difference} and rely on the parallel trends assumption to identify treatment effects that are robust to heterogeneous treatment effects across time and treatment-timing groups.
However, we acknowledge that we did not rigorously test for endogeneity, as both treatments are self-selected.
For example, although we include multiple treatment-timing groups, our short-term sample periods cannot fully avoid contemporaneous factors at the annual level that affect treatment adoption and outcomes simultaneously.
Future research should consider instrumental variable approaches to address these endogeneity concerns more rigorously.
